---
title: "ASD-descriptive"
author: "Søren"
date: "2023-12-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
p_load("tidyverse", "gt", "gtExtras", "DiagrammeR", "DiagrammeRsvg", "webshot")
```

```{r}
setwd('.')
df <- read_csv("../data/Eye-tracking Output/cleaned_data.csv") 
```

```{r}
# Load necessary libraries
library(dplyr)
library(gt)

# Assuming 'df' is your dataframe

# Creating a subset with unique participants
unique_participants_df <- df %>% distinct(Participant, .keep_all = TRUE)

# Calculate mean and SD for age
mean_age <- mean(unique_participants_df$Age, na.rm = TRUE)
sd_age <- sd(unique_participants_df$Age, na.rm = TRUE)

# Count unique participants for each gender
unique_gender_counts <- unique_participants_df %>% 
  group_by(Gender) %>% 
  summarise(Count = n())

# Count unique participants for each class (ASD or TD)
unique_class_counts <- unique_participants_df %>% 
  group_by(Class) %>% 
  summarise(Count = n())

# CARS score stats for ASD participants
mean_cars_score <- mean(unique_participants_df[unique_participants_df$Class == 'ASD',]$`CARS Score`, na.rm = TRUE)
sd_cars_score <- sd(unique_participants_df[unique_participants_df$Class == 'ASD',]$`CARS Score`, na.rm = TRUE)

# Total number of unique participants
n_participants <- n_distinct(unique_participants_df$Participant)

# Number of unique stimuli
n_unique_stimuli <- n_distinct(df$Stimulus)

# Create a summary table using gt
summary_table <- tibble(
  Statistic = c("Mean Age of Participants", "Gender Distribution - Male", "Gender Distribution - Female",
                "Class Distribution - ASD", "Class Distribution - TD",
                "Mean CARS Score for ASD", "Total Unique Participants", "Number of Unique Stimuli"),
  Value = c(sprintf("%.2f (SD: %.2f) years", mean_age, sd_age),
            unique_gender_counts[unique_gender_counts$Gender == "M",]$Count,
            unique_gender_counts[unique_gender_counts$Gender == "F",]$Count,
            unique_class_counts[unique_class_counts$Class == "ASD",]$Count,
            unique_class_counts[unique_class_counts$Class == "TD",]$Count,
            ifelse(is.na(mean_cars_score), "NA", sprintf("%.2f (SD: %.2f)", mean_cars_score, sd_cars_score)),
            n_participants,
            n_unique_stimuli)
) %>%
  gt() %>%
  gt_theme_nytimes() %>% 
  tab_header(
    title = "Summary Statistics of Eye-tracking Dataset"
  ) %>%
  cols_label(
    Statistic = "Statistic",
    Value = "Value"
  )
# Print the summary table
print(summary_table)

# Export the table as a PNG file
gt::gtsave(summary_table, filename = "../data/summary_table.png")

# Alternatively, export as HTML if preferred
#gt::gtsave(styled_table, filename = "summary_table.html")

```
```{r}
# Load necessary libraries
library(dplyr)
library(gt)

# Assuming 'df' is your dataframe

# Creating a subset with unique participants
unique_participants_df <- df %>% distinct(Participant, .keep_all = TRUE)

# Calculate mean and SD for age
mean_age <- mean(unique_participants_df$Age, na.rm = TRUE)
sd_age <- sd(unique_participants_df$Age, na.rm = TRUE)

# Count unique participants for each gender
unique_gender_counts <- unique_participants_df %>% 
  group_by(Gender) %>% 
  summarise(Count = n())

# Gender difference in ASD
asd_gender_distribution <- unique_participants_df %>% 
  filter(Class == "ASD") %>%
  group_by(Gender) %>%
  summarise(ASD_Count = n())

# Merge gender counts with ASD gender distribution
gender_asd_distribution <- left_join(unique_gender_counts, asd_gender_distribution, by = "Gender")

# Format gender distribution with ASD count
gender_asd_distribution$Formatted <- paste(gender_asd_distribution$Gender, gender_asd_distribution$Count, "(ASD:", gender_asd_distribution$ASD_Count, ")")

# Count unique participants for each class (ASD or TD)
unique_class_counts <- unique_participants_df %>% 
  group_by(Class) %>% 
  summarise(Count = n())

# CARS score stats for ASD participants
mean_cars_score <- mean(unique_participants_df[unique_participants_df$Class == 'ASD',]$`CARS Score`, na.rm = TRUE)
sd_cars_score <- sd(unique_participants_df[unique_participants_df$Class == 'ASD',]$`CARS Score`, na.rm = TRUE)

# Total number of unique participants
n_participants <- n_distinct(unique_participants_df$Participant)

# Number of unique stimuli
n_unique_stimuli <- n_distinct(df$Stimulus)

# Create a summary table using gt
summary_table <- tibble(
  Statistic = c("Total Unique Participants", 
                "Class Distribution - ASD", 
                "Class Distribution - TD",
                "Gender Distribution - Female", 
                "Gender Distribution - Male",
                "Mean Age of Participants", 
                "Mean CARS Score for ASD", 
                "Number of Unique Stimuli"),
  Value = c(n_participants,
            unique_class_counts[unique_class_counts$Class == "ASD",]$Count,
            unique_class_counts[unique_class_counts$Class == "TD",]$Count,
            gender_asd_distribution[gender_asd_distribution$Gender == "F",]$Formatted,
            gender_asd_distribution[gender_asd_distribution$Gender == "M",]$Formatted,
            sprintf("%.2f (SD: %.2f) years", mean_age, sd_age),
            ifelse(is.na(mean_cars_score), "NA", sprintf("%.2f (SD: %.2f)", mean_cars_score, sd_cars_score)),
            n_unique_stimuli)
) %>%
  gt() %>%
  gt_theme_nytimes() %>% 
  tab_header(
    title = "Summary Statistics of Eye-tracking Dataset"
  ) %>%
  cols_label(
    Statistic = "Statistic",
    Value = "Value"
  )

# Print the summary table
print(summary_table)

# Export the table as a PNG file
gt::gtsave(summary_table, filename = "../data/summary_table.png")

# Alternatively, export as HTML if preferred
#gt::gtsave(summary_table, filename = "summary_table.html")

```


```{r}
# Load the necessary library
library(gt)

# Define the scores directly
scores_df <- data.frame(
  Metric = c("Accuracy", "F1 Score", "Sensitivity", "Specificity"),
  Score = c("83.94% (95% CI: 0.71 - 0.97)", "85.69% (95% CI: 0.75 - 0.96)", "86.48% (95% CI: 0.78 - 0.95)", "80.00% (95% CI: 0.56 - 1.00)")
)

# Create a summary table using gt
summary_table <- scores_df %>%
  gt() %>%
  gt_theme_nytimes() %>% 
  tab_header(
    title = "Summary of Model Performance Scores"
  ) %>%
  cols_label(
    Metric = "Metric",
    Score = "Score"
  )

# Print the summary table
print(summary_table)

# Optional: Export the table as a PNG file
gt::gtsave(summary_table, filename = "../data/model_performance_scores.png")
```

```{r}
confusion_matrix <- matrix(c(4, 24, 23, 5), nrow = 2, byrow = TRUE)

# Add row and column names for clarity
rownames(confusion_matrix) <- c("ASD", "TD")
colnames(confusion_matrix) <- c("Predicted TD", "Predicted ASD")

# Convert matrix to dataframe for ggplot
confusion_df <- as.data.frame(as.table(confusion_matrix))

# Plotting the confusion matrix
ggplot(data = confusion_df, aes(x = Var1, y = Var2, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%0.0f", Freq)), vjust = 1) +
  scale_fill_gradient(low = "white", high = "steelblue") +
  labs(title = "Confusion Matrix for ASD vs TD Prediction", x = "Actual Class", y = "Predicted Class") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  
```


```{r}
library(DiagrammeR)

grViz("
digraph flowchart {

  # Define nodes
  node [shape=box]
  A[label='Dataset']
  B[label='Pre-processing']
  C[label='Train Dataset']
  D[label='Test Dataset']
  E[label='Validation Dataset']
  F[label='Model']
  G[label='Evaluation Parameters\n-Accuracy\n-Precision\n-Recall']
  H[label='Validation\n-K-Fold']
  I[label='Output']
  J[label='Prediction\n-ASD\n-TC']

  # Connect nodes
  A -> B -> {C D E}
  C -> F -> G -> H -> I -> J

  # Subgraph for preprocessing steps
    subgraph cluster_0 {
    label='Preprocessing Steps'
    P1[label='-Missing values Imputation\n-Scaling\n-SMOT\n-Outliers Removal\n-Sequential Forward Selection']
  }

  # Connect preprocessing subgraph to main flow
  B -> P1
  
}
")


```

\text{Accuracy} = \frac{\text{True Positives (TP)} + \text{True Negatives (TN)}}{\text{Total Observations}}
\text{Sensitivity} = \frac{\text{True Positives (TP)}}{\text{True Positives (TP)} + \text{False Negatives (FN)}}
\text{Specificity} = \frac{\text{True Negatives (TN)}}{\text{True Negatives (TN)} + \text{False Positives (FP)}}
\text{F1 Score} = 2 \times \frac{\text{Precision} \times \text{Sensitivity}}{\text{Precision} + \text{Sensitivity}}
\text{Precision} = \frac{\text{True Positives (TP)}}{\text{True Positives (TP)} + \text{False Positives (FP)}}


